Re-Examine Hybrid State-Space and Self-Attention for In-Context Learning

### 2025-01-24 paper.tex
Updated Author list

@@

% Todonotes is useful during development; simply uncomment the next line
%    and comment out the line below the next line to turn off comments
%\usepackage[disable,textsize=tiny]{todonotes}
\usepackage[textsize=tiny]{todonotes}

% The \icmltitle you define below is probably too long as a header.
% Therefore, a short form for the running title is supplied here:
\icmltitlerunning{OTCE: Hybrid SSM and Attention with Cross Domain Mixture of Experts to construct Observer-Thinker-Conceiver-Expresser for ICML 2025}

@@

\begin{icmlauthorlist}
\icmlauthor{Jingze Shi}{equal,yyy}
\icmlauthor{Bingheng Wu}{equal,yyy,comp}

%\icmlauthor{}{sch}
%\icmlauthor{}{sch}
\end{icmlauthorlist}

\icmlaffiliation{yyy}{Department of XXX, University of YYY, Location, Country}
\icmlaffiliation{comp}{Company Name, Location, Country}
\icmlaffiliation{sch}{School of ZZZ, Institute of WWW, Location, Country}

\icmlcorrespondingauthor{Firstname1 Lastname1}{first1.last1@xxx.edu}
\icmlcorrespondingauthor{Firstname2 Lastname2}{first2.last2@www.uk}

>>>>

% % For code
% \usepackage{listings}
% \usepackage[frozencache,cachedir=.]{minted}

@@

% Todonotes is useful during development; simply uncomment the next line
%    and comment out the line below the next line to turn off comments
%\usepackage[disable,textsize=tiny]{todonotes}
% \usepackage[textsize=tiny]{todonotes}

% The \icmltitle you define below is probably too long as a header.
% Therefore, a short form for the running title is supplied here:
\icmltitlerunning{Re-Examine Hybrid State-Space and Self-Attention for In-Context Learning}

@@

\begin{icmlauthorlist}
\icmlauthor{Jingze Shi}{equal,IR}
\icmlauthor{Bingheng Wu}{equal,IR}
\end{icmlauthorlist}

\icmlaffiliation{IR}{Independent Researcher}

\icmlcorrespondingauthor{Jingze Shi}{losercheems@gmail.com}
\icmlcorrespondingauthor{Bingheng Wu}{wubingheng52136@gmail.com}
